---
title: Robert Pikmets's CV"
author: Robert Pikmets
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---


```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')


# First let's get the data, filtering to only the items tagged as
# Resume items
position_data <- read_csv('mypositions.csv') %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('work_experience', 'industry_positions') ~ 'positions', 
      section %in% c('extra', 'by_me_press') ~ 'extra',
      TRUE ~ section
    )
  ) 

```


Main
================================================================================

Robert Pikmets {#title}
--------------------------------------------------------------------------------

<pre style="font:inherit">
<i class="fa fa-envelope"></i> robertpikmets@gmail.com      <i class="fab fa-linkedin-in"></i> linkedin.com/in/robert-pikmets      <i class="fa fa-github"></i> github.com/robertpikmets      <i class="fa fa-phone"></i> +372 5332 7319
</pre>

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```



Work Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('positions')
```

Extracurricular activities {data-icon=chess-knight}
--------------------------------------------------------------------------------


```{r}
position_data %>% print_section('extra')
```


Skills  {data-icon=laptop}
--------------------------------------------------------------------------------

<div class="tech">
- <b>Languages</b> - R, Python, SQL, VBA, MATLAB
- <b>Machine learning and modelling</b> - Regression, classification, clustering, deep learning, feature engineering, regularization methods, time series models. Experience with Skicit-learn, Keras, Tensorflow.
- <b>Data analysis</b> - Retrieving data with SQL, pre-processing and manipulation (dplyr in R and pandas in Python), visualisation and presenting using ggplot2 and RMarkdown (even this CV is automated with R and R Markdown)
- <b>Statistics</b> - Statistical inference, descriptive statistics, hypothesis testing
</div>
